---
title: "Final Project"
author: "You Li"
date: "4/27/2019"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Load necessary packages here.

```{r}
library(readr)
library(ggformula)
library(dplyr)
library(stringr)
```

read all csv files here
```{r}
NY_VS_LA=read_csv('NYC_VS_LA.csv')
NYC_TOP10=read_csv('NYC_TOP10.csv')
LA_TOP10=read_csv('LA_TOP10.csv')
place_sentiment_rate=read_csv('place_sentiment rate.csv')
```

Let's use t-test to test whether the sentiment rate of New York City tweets are different from that of Los Angeles tweets.

H_0:  mu_NYC = mu_LA
H_a:  mu_NYC != mu_LA

```{r}
t.test(NY_VS_LA$NYC, NY_VS_LA$LA, alternative="two.sided")
```
Conclusion: There is no enough evidence at the 0.05 significance level to claim that the sentiment rates of New York City tweets are different from that of Los Angeles tweets. However, the P value is very closed to 0.05.

Let's see how many tweets related to NYC are possitive, how many are negative, how many are neutral?
```{r}
length(which(NY_VS_LA$NYC>0))
length(which(NY_VS_LA$NYC==0))
length(which(NY_VS_LA$NYC<0))
```
How many tweets related to LA are possitive, how many are negative, how many are neutral?
```{r}
length(which(NY_VS_LA$LA>0))
length(which(NY_VS_LA$LA==0))
length(which(NY_VS_LA$LA<0))
```
Compare the positive sentiment rates of tweets related to NYC and LA.
```{r}
summary(NY_VS_LA$NYC[which(NY_VS_LA$NYC>0)])
summary(NY_VS_LA$LA[which(NY_VS_LA$LA>0)])
```
Compare the negative sentiment rates of tweets related to NYC and LA.
```{r}
summary(NY_VS_LA$NYC[which(NY_VS_LA$NYC<0)])
summary(NY_VS_LA$LA[which(NY_VS_LA$LA<0)])
```

Create a histogram to check the distribution of sentiment rates
```{r}
gf_histogram(~NYC, data=NY_VS_LA) %>%
  gf_labs(title="Sentiment Rate Distribution of the Tweets Related to NYC")
```
```{r}
gf_histogram(~LA, data=NY_VS_LA) %>%
  gf_labs(title="Sentiment Rate Distribution of the Tweets Related to LA")
```
Use 1,0 (True/False) create a binary classification to distinguish residents and tourists.

New York City includes five parts:Manhattanm, Brooklyn, Queens, Bronx and Staten Island. So people who are in these places are "New York City" residents.
```{r}
NewYorkCity<-'(Manhattan, NY)|(Brooklyn, NY)|(Queens, NY)|(Bronx,NY)|(Staten Island,NY)|(New York, NY)'
place_sentiment_rate<-
  place_sentiment_rate%>%
  mutate(NYC_residents_tourists=ifelse(str_detect(place_sentiment_rate$NYC_placed_tweets,NewYorkCity)==TRUE,1,0))%>%
  mutate(LA_residents_tourists=ifelse(str_detect(place_sentiment_rate$LA_placed_tweets,"Los Angeles, CA")==TRUE,1,0))
```

Compare the sentiment rate from NYC residents' tweets and tourists' tweets
```{r}
NYC_residents=(place_sentiment_rate$NYC_placed_tweets_sentiment[which(place_sentiment_rate$NYC_residents_tourists==1)])
NYC_tourists=(place_sentiment_rate$NYC_placed_tweets_sentiment[which(place_sentiment_rate$NYC_residents_tourists==0)])
summary(NYC_residents)
summary(NYC_tourists)
```
H_0:  mu_NYC = mu_NYC_residents
H_a:  mu_NYC != mu_NYC_residents
The null hypothesis is that there is no difference between the sentiment rates of NYC tweets and the sentiment rates of NYC residents' tweets.

```{r}
t.test(NY_VS_LA$NYC, NYC_residents, alternative="two.sided")
```
Conclusion:This is no enough evidence  at the 0.05 significance level to claim that the sentiment rates of NYC tweets are different the sentiment rates of NYC residents' tweets.


H_0:  mu_NYC = mu_NYC_tourists
H_a:  mu_NYC != mu_NYC_tourists
The null hypothesis is that there is no difference between the sentiment rates of NYC tweets and the sentiment rates of NYC tourists' tweets.
```{r}
t.test(NY_VS_LA$NYC, NYC_tourists, alternative="two.sided")
```
Conclusion:This is enough evidence  at the 0.05 significance level to claim that the sentiment rates of NYC tweets are different the sentiment rates of NYC tourists' tweets.

Compare the sentiment rate from LA residents' tweets and tourists' tweets
```{r}
LA_residents=(place_sentiment_rate$LA_placed_tweets_sentiment[which(place_sentiment_rate$LA_residents_tourists==1)])
LA_tourists=(place_sentiment_rate$LA_placed_tweets_sentiment[which(place_sentiment_rate$LA_residents_tourists==0)])
summary(LA_residents)
summary(LA_tourists)
```

H_0:  mu_LA = mu_LA_residents
H_a:  mu_LA != mu_LA_residents
The null hypothesis is that there is no difference between the sentiment rates of LA tweets and the sentiment rates of LA residents' tweets.
```{r}
t.test(NY_VS_LA$LA, LA_residents, alternative="two.sided")
```
Conclusion:This is no enough evidence  at the 0.05 significance level to claim that the sentiment rates of LA tweets are different the sentiment rates of LA residents' tweets.

H_0:  mu_LA = mu_LA_tourists
H_a:  mu_LA != mu_LA_tourists
The null hypothesis is that there is no difference between the sentiment rates of LA tweets and the sentiment rates of LA tourists' tweets.
```{r}
t.test(NY_VS_LA$LA, LA_tourists, alternative="two.sided")
```
Conclusion:This is no enough evidence  at the 0.05 significance level to claim that the sentiment rates of LA tweets are different the sentiment rates of LA tourists' tweets.


At last, let's create a graph for top 10 words of each city. We can see which word is the most frequency word in the graph, and we also can see what the category of the word.
```{r}
NYC_TOP10$category[which(NYC_TOP10$category=='NNP')]='proper noun'
NYC_TOP10$category[which(NYC_TOP10$category=='PRP')]='personal pronoun'
NYC_TOP10$category[which(NYC_TOP10$category=='PRP$')]='possessive pronoun'
NYC_TOP10$category[which(NYC_TOP10$category=='VBZ')]='verb'
```

```{r}
NYC_TOP10%>%
  mutate(word=reorder(word,count))%>%
  gf_col(count~word,fill=~ category, data=NYC_TOP10) %>%
  gf_labs(title="NYC Top 10 Words")
```
```{r}
LA_TOP10$category[which(LA_TOP10$category=='JJ')]='adjective'
LA_TOP10$category[which(LA_TOP10$category=='NN')]='proper noun'
LA_TOP10$category[which(LA_TOP10$category=='PRP')]='personal pronoun'
LA_TOP10$category[which(LA_TOP10$category=='PRP$')]='possessive pronoun'
LA_TOP10$category[which(LA_TOP10$category=='VBZ')]='verb'
LA_TOP10$category[which(LA_TOP10$category=='VBP')]='verb'
LA_TOP10$category[which(LA_TOP10$category=='VB')]='verb'
```

```{r}
LA_TOP10%>%
  mutate(word=reorder(word,count))%>%
  gf_col(count~word,fill=~ category,data=LA_TOP10) %>%
  gf_labs(title="LA Top 10 Words")
```

